Title

### 2013-03-05 inc/extension/liouvilles_theorem/liouvilles_theorem.tex
merge the rest of the comments from andreas in sections 2-3.2

In the transverse dimension, this is consistent with the definition of `coherent fluence' employed by Reed et al.\cite{reed_evolution_2009} for time-resolved electron microscopy and, of course, the spatial emittance of an electron beam \cite{jensen_theoretical_2006,siwick_ultrafast_2002}.

>>>>

We note that, in the transverse directions ($\smallT$), this is consistent with the definition of `coherent fluence' employed by Reed et al.\cite{reed_evolution_2009} for time-resolved electron microscopy and, of course, the trasverse spatial emittance of an electron beam \cite{jensen_theoretical_2006,siwick_ultrafast_2002}.
%TODO include more commentary on $\varepsilon_{\smallT}$?
